---
title: "5100_project"
output: html_document
date: "2023-11-21"
---
```{r}
df=read.csv('Income_Inequality_clean.csv')
```
```{r}
library(dplyr)
```

# Region and quintile of Income
```{r}
 region_df<- df %>%
  select(Region, Q1,Q2,Q3,Q4,Q5)%>%
  group_by(Region) 
```

```{r}
region_df
```
```{r}
asia <- subset(region_df, Region == "Asia")
europe <- subset(region_df, Region == "Europe")
americas <- subset(region_df, Region == "Americas")
africa <- subset(region_df, Region == "Africa")
```

```{r}
q5 <- list(asia$Q5,europe$Q5,americas$Q5,africa$Q5)
boxplot(q5,names=c('Aisa','Europe','Americas','Africa'),main= 'Upper quintile of Incomes',col = '#ec6337',xlab = "Countries", ylab = "Quintile 5")
```

 As shown, in Africa those 20% percentage of people has larger income share
```{r}
summary(asia$Q5)
```

```{r}
summary(europe$Q5)
```


```{r}
summary(americas$Q5)
```

```{r}
summary(africa$Q5)
```
```{r}
summary(asia$Q5)
summary(europe$Q5)
summary(americas$Q5)
summary(africa$Q5)
```



```{r}
q1 <- list(asia$Q1,europe$Q1,americas$Q1,africa$Q1)
boxplot(q1,names=c('Aisa','Europe','Americas','Africa'),main= 'Lower quintile of Incomes',col = '#ec6337',xlab = "Countries", ylab = "Quintile 1")
```
```{r}
summary(asia$Q1)
summary(europe$Q1)
summary(americas$Q1)
summary(africa$Q1)
```

# Null hypothesis


H0: Americas's upper quintile poupulation of income shares = Asia's upper quintile population of income shares


Ha: Americas's upper quintile poupulation of income shares > Asia's upper quintile population of income shares

# t test
```{r}
asia_q5= subset(asia, select=Q5, drop=T)
americas_q5= subset(americas, select=Q5, drop=T)
t.test(americas_q5,asia_q5, alt="greater",conf.level=.95)
```

# bootstrap
```{r}
# Perform a bootstrap test for ratio of means of Q5
set.seed(1000)
N <- 10000
ratio_mean_boot <- numeric(N) 

for (i in 1:N)
{
americas_sample <- sample(americas_q5, length(americas_q5), replace = TRUE) 
asia_sample <- sample(asia_q5, length(asia_q5), replace = TRUE)
ratio_mean_boot[i] <- mean(americas_sample) / mean(asia_sample)
}
boot_mean<- mean(ratio_mean_boot)
cat("Bootstrap Mean:",boot_mean, "\n")
# one tail
confidence_interval<- quantile(ratio_mean_boot, 0.05)
cat("Bootstrap 95% Confidence Interval for the Mean:", confidence_interval, "\n")
bootstrap_variance = var(ratio_mean_boot)
cat("Bootstrap variance for the Mean:",bootstrap_variance, "\n")
```

```{r}
# one tail
quantile(ratio_mean_boot, 0.05)
```
```{r}
bootstrap_variance = var(ratio_mean_boot)
bootstrap_variance
```
Vairance is a small value like 3.736707e-05 suggests a relatively stable estimate.

Since 1 is not in the 95% bootstrap confidence bound,reject the null hypothesis.
So, we can conclude that America's upper quintile population of income shares Asia's upper quintile population of income shares. which means 20% of America people has higher income percentage than the Asias. Which means, the wealthy people in America control comparably more money than wealthy people in Asia.